High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-05 notebooks/gmsc.qmd
tried large ensemble (good), large regularized ensemble (poor). First steps for CNN

@@

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 250])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser =  Flux.softmax                       # finaliser function
```

>>>>

## Additional feature preprocessing

```{julia}
pre_proc = false
if pre_proc
    Xmat = matrix(X)

    function threshold(x)
        σ = std(x)
        return -2σ .< x .< 2σ
    end
    mask = reduce(hcat, map(x -> threshold(x), eachcol(Xmat)))
    keep_rows = map(x -> all(x), eachrow(mask))
    Xmat = Xmat[keep_rows,:]
    labels = labels[keep_rows]

    function boxcox(x)
        transf = MLJ.UnivariateBoxCoxTransformer()
        x = exp.(x)
        mach = machine(transf, x)
        fit!(mach)
        z = MLJ.transform(mach, x)
        return z
    end
    Xmat = reduce(hcat, map(x -> boxcox(x), eachcol(Xmat)))
    X = table(Float32.(Xmat))
end
```

@@

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 250])
n_hidden = 32
activation = Flux.relu
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy            # loss function
_finaliser =  Flux.softmax                  # finaliser function
```

### 2023-08-05 notebooks/mnist.qmd
tried large ensemble (good), large regularized ensemble (poor). First steps for CNN

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finaliser function
```

@@

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.1,0.25,0.25],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
)

@@

    for (_name,ce) in collect(ces)[_plt_order]
        _x = CounterfactualExplanations.counterfactual(ce)
        _phat = target_probs(ce)
        _title = "($(letters[_count]))"
        plt = Plots.plot(
            convert2image(MNIST, reshape(_x,28,28)),
            axis=([], false), 
            size=(img_height, img_height),
            title=_title
        )
        plts = [plts..., plt]
        _count += 1
    end
    plt = Plots.plot(plts...; size=(img_height,img_height))

@@

@@

# Deep Ensemble:
mlp_large_ens = EnsembleModel(model=mlp, n=50)

add_models = Dict(
    "Large MLP Ensemble" => mlp_large_ens,
)

@@

```{julia}
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = ["MLP", "MLP Ensemble", "Large Ensemble" "JEM", "JEM Ensemble"]
)
display(plt_additional_models)
savefig(plt, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

>>>>

```{julia}
# Model parameters:
epochs = 10
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finaliser function
```

@@

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.1,0.25,0.25],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
    model_dict=model_dict,
    wide::Bool = false,
)

@@

    for (_name,ce) in collect(ces)[_plt_order]
        _x = CounterfactualExplanations.counterfactual(ce)
        _phat = target_probs(ce)
        _title = "($(letters[_count]))"
        plt = Plots.plot(
            convert2image(MNIST, reshape(_x,28,28)),
            axis=([], false), 
            size=(img_height, img_height),
            title=_title
        )
        plts = [plts..., plt]
        _count += 1
    end
    if wide
        plt = Plots.plot(plts...; size=(img_height*length(plts),img_height), layout=(1,length(plts)))
    else
        plt = Plots.plot(plts...; size=(img_height,img_height))
    end

@@

An MLP with regularization:

```{julia}
mlp_reg = NeuralNetworkClassifier(
    builder=builder, 
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
    lambda=1.0,
    alpha=0.5,
)
```

A CNN:

```{julia}
mutable struct MyConvBuilder
	filter_size::Int
	channels1::Int
	channels2::Int
	channels3::Int
end

function MLJFlux.build(b::MyConvBuilder, rng, n_in, n_out, n_channels)

	k, c1, c2, c3 = b.filter_size, b.channels1, b.channels2, b.channels3

	mod(k, 2) == 1 || error("`filter_size` must be odd. ")

	# padding to preserve image size on convolution:
	p = div(k - 1, 2)

	front = Chain(
			   Conv((k, k), n_channels => c1, pad=(p, p), relu),
			   MaxPool((2, 2)),
			   Conv((k, k), c1 => c2, pad=(p, p), relu),
			   MaxPool((2, 2)),
			   Conv((k, k), c2 => c3, pad=(p, p), relu),
			   MaxPool((2 ,2)),
			   flatten)
	d = Flux.outputsize(front, (n_in..., n_channels, 1)) |> first
	return Chain(front, Dense(d, n_out))
end

clf = ImageClassifier(builder=MyConvBuilder(3, 16, 32, 32),
					  epochs=10,
					  loss=Flux.crossentropy)
function toimg(X)
    X = MLUtils.stack(map(x -> reshape(x, 28,28), eachrow(matrix(X))))
    X = coerce(X, GrayImage)
    return X
end
clf = (X -> toimg(X)) |> clf
```

@@

# Deep Ensemble:
mlp_large_ens = EnsembleModel(model=mlp, n=50)
mlp_drop_large_ens = EnsembleModel(model=mlp_reg, n=50)

add_models = Dict(
    "Large Ensemble" => mlp_large_ens,
    "Large Ensemble Reg" => mlp_drop_large_ens,
)

@@

```{julia}
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = ["MLP", "MLP Ensemble", "Large Ensemble", "Large Ensemble Reg", "JEM", "JEM Ensemble"],
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt, joinpath(output_images_path, "mnist_eccco_additional.png"))
```
